### 2018-03-08 introduction/intro.tex
Outline abstract/Intro. Add rough title

\section{Part I}

The introduction to your thesis goes here.

\section{Part II}
More intro!

\section{Part III}
Even more intro.

>>>>

\section{Gravitational Waves}
\label{sec:intro_gw}
Brief introduction to GW stuff.

\subsection{GW Detectors}
\label{sec:intro_gw_det}
Brief talk about LIGO and Virgo

\subsection{GW Sources}
\label{sec:intro_gw_source}
Brief talk about expected sources for LIGO

\section{Joint GW-EM Astronomy}
\label{sec:intro_joint}
Talk about why we want to do joint GW-EM astronomy. What are the science gains and limitations of individual detections vs. Joint

\subsection{EM Counterparts}
\label{sec:intro_counterparts}
Talk about each of the EM counterparts across the spectrum. Perhaps one subsection per?

\subsection{Search Methods}
\label{sec:intro_searchmethods}
Let's talk about how to find these things eh

Large localization regions!

\subsubsection{Galaxy-Targeted}
\label{sec:intro_galaxy}
Galaxy targeted searches. Pros and Cons.

\subsubsection{Wide-Field Searches}
\label{sec:intro_widefield}
Wide-field seachres. Pros and Cons.

Issues of contamination abound.

\section{History of Detections}
\label{sec:intro_history}
A little history of LIGO observing runs and status.

\subsection{GW150914: The First Detection}
\label{sec:intro_gw150914}
A bit on GW150914, the first detection, the \fermi stuff, etc.

\subsection{Binary Black Holes. So Many.}
Continued detection of BBHs

Virgo joining aLIGO. GW170814

\subsection{GW170817: The Dawn of Joint GW-EM Astronomy}
The detection of GW170817. The GRB. Optical counterpart and observations. Radio and X-Ray stuff.

Brief outline of thesis? Highlight tackling both issues of contamination and detection/follow-up in practice.
